### 2012-03-09 doc/theses/mikula/proposed_algorithm.tex
Master thesis: In progress.

Additionally, \texttt{PathType} contains a list of special functions that were called with an argument of \texttt{PathType} type. The motivation is that in some cases of function calls, we want to know that the function call is performed with an instance of \texttt{PathType} because then, we can determine a type of the function call more precisely. Those special functions are built-in functions \texttt{data}, \texttt{min}, \texttt{max} \todo{Doplnit}.

@@

\subsection{Determination of Global Variable Types}
A similar approach as in the case of functions can be applied to determine types of global variables. Alike the functions, the global variables are defined in the prolog section. A type of a variable can be explicitly specified in its definition \todo{je to tak? priklad}. If it is not, it may often be deducible from the binding expression. Again, we do not analyse external variables for the same reason as in case of external functions.

@@

\todo[inline]{Overit si, ci ALG \ref{ALG_func_analysisOfExpressionTypes} pokryva vsetky pripady, co sa tyka definovania novych premennych a ich propagacie vyssim uzlom.}

\todo[inline]{Pozor na to přetékání textu - na spoustě míst.}

@@

The output of this step is a set of couples ($pathType$, XML Schema built-in type).

\todo[inline]{Zlucovanie odvodenych tvrdeni.}
\todo[inline]{Path expressions s predikatmi.}

>>>>

Additionally, \texttt{PathType} contains a list of special functions that were called with an argument of \texttt{PathType} type. The motivation is that in some cases of function calls, we want to know that the function call is performed with an instance of \texttt{PathType} because then, we can determine a type of the function call more precisely. Those special functions are built-in functions \texttt{data}, \texttt{min}, \texttt{max}, \texttt{avg}, \texttt{sum}, \texttt{distinct-values}.

@@

\subsection{Determination of Global Variable Types}
A similar approach as in the case of functions can be applied to determine types of global variables. Alike the functions, the global variables are defined in the prolog section. A type of a variable can be explicitly specified in its definition, for instance \texttt{declare variable \$x as xs:byte := 12;}. If it is not, it may often be deducible from the binding expression. Again, we do not analyse external variables for the same reason as in case of external functions.

@@

@@

The output of this step is a set of statements of form \\ an instance of \texttt{PathType} $\rightarrow$ XML Schema built-in atomic type.
